% \documentclass[11pt,letterpaper,roman,colorlinks=true]{moderncv}
\documentclass[11pt]{article}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[margin=.75in, bmargin=.9in]{geometry}

% use linux libertine as the serif font / linux biolinum as the sans serif font
\usepackage[tt=false, type1=true]{libertine}
\usepackage[varqu]{zi4}
\usepackage[libertine]{newtxmath}

% use charter as the font
% \usepackage[bitstream-charter]{mathdesign}
% \usepackage[T1]{fontenc}

\RequirePackage{fontawesome} % logo font

\usepackage{xcolor}
\definecolor{accent}{HTML}{007985}
\definecolor{color0}{rgb}{0,0,0}% black
\colorlet{color1}{accent}% accent
\definecolor{color2}{rgb}{0.35,0.35,0.35}% dark grey

\usepackage{enumitem}
\usepackage{etaremune} % reversed-order lists
% print brackets around list index
% https://tex.stackexchange.com/a/428870
\renewcommand*{\labelenumi}{[\theenumi]}

% for some reason this has to go inside document when using moderncv
% https://tex.stackexchange.com/a/572408
\usepackage[colorlinks]{hyperref}
\AtBeginDocument{%
\hypersetup{
  urlcolor={color2},
  linkcolor={color2},
}
}

% turn off links to bib which cause problems when the CV is included in the same PDF as my research statement
% https://tex.stackexchange.com/questions/662944/remove-clickable-links-on-citations-to-the-bibliography
\makeatletter
\renewcommand\hyper@natanchorstart[1]{} 
\renewcommand\hyper@natanchorend{} 
\renewcommand\hyper@natlinkstart[1]{} 
\renewcommand\hyper@natlinkend{} 
\renewcommand\hyper@natlinkbreak[2]{#1}
\makeatother



%== page numbers
% https://tex.stackexchange.com/a/153176
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{} % Clear the header and footer
\fancyfoot{}
\fancyfoot[R]{\thepage} % Number pages at right foot
\renewcommand{\headrulewidth}{0pt} % Don't draw line at top

%=== bibliography stuff
\usepackage[
            datamodel=acmdatamodel, % acm stuff
            sorting=none,        % show refs in text order
            style=acmauthoryear,
            % bibstyle=numeric,    % number refs
            giveninits=false,    % print full author names
            maxbibnames=99,      % list all author names in references
            maxcitenames=99      % list all author names in citations (since our styled references are secretly citations)
           ]{biblatex}

% \DeclareNameAlias{default}{given-family}
% \DeclareNameAlias{sortname}{given-family}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

\newcommand{\me}[1]{\textbf{#1}}
\newcommand{\HonorableMention}[1]{{\href{#1}{\color{accent}[Best Paper, Honorable Mention]}}}

% highlight name in references based on "highlight" annotation from bib file
% https://tex.stackexchange.com/a/304968
\renewcommand*{\mkbibnamegiven}[1]{%
  \ifitemannotation{highlight}
    {\me{#1}}
    {#1}}

\renewcommand*{\mkbibnamefamily}[1]{%
  \ifitemannotation{highlight}
    {\me{#1}}
    {#1}}

\newcommand{\nameuse}[1]{%
  \def\do##1{\settoggle{blx@use##1}{#1}}%
  \dolistcsloop{blx@datamodel@names}
  }

%=== Custom cite command with a newline for authors and journal

% https://tex.stackexchange.com/a/401936
\DeclareCiteCommand{\rawcvcite}
  {\usebibmacro{prenote}}
  {\printnames{author}. \usebibmacro{year}
   \newline\nopunct\newblock
   \usebibmacro{maintitle+title}%
   \setunit{\addspace}\usebibmacro{addendum+pubstate}%
   \newline\nopunct\newblock
   \usebibmacro{journal+issuetitle}%
   \usebibmacro{year}%
   \usebibmacro{doi+eprint+url}
  }
  {\multicitedelim}
  {\usebibmacro{postnote}}

% use minipage to vertically center enumeration label next to citation
\newcommand{\cvcite}[1]{
    \begin{minipage}{\linewidth}
    \rawcvcite{#1}
    \end{minipage}
}

% format the titles in italics
\DeclareFieldFormat
  [article,book,inbook,incollection,inproceedings,patent,thesis,unpublished]
  {title}{{\textit{#1}}}
\DeclareFieldFormat
  [article,book,inbook,incollection,inproceedings,patent,thesis,unpublished]
  {journaltitle}{{{#1}}}

% use title case
\DeclareFieldFormat{titlecase}{#1}

%=== number refs in reverse order https://tex.stackexchange.com/a/22770
% Count total number of entries in each refsection
\AtDataInput{%
  \csnumgdef{entrycount:\therefsection}{%
    \csuse{entrycount:\therefsection}+1}}

% Print the labelnumber as the total number of entries in the
% current refsection, minus the actual labelnumber, plus one
\DeclareFieldFormat{labelnumber}{\mkbibdesc{#1}}    
\newrobustcmd*{\mkbibdesc}[1]{%
  \number\numexpr\csuse{entrycount:\therefsection}+1-#1\relax}

%==== moderncv themes
% \moderncvstyle{classic}
%\nopagenumbers{}

\newcommand{\cvindent}[1]{
% https://tex.stackexchange.com/a/35936
\hspace*{1em}
\begin{minipage}{\dimexpr\textwidth-1em}
#1
\end{minipage}
}

\newcommand{\shortcventry}[6]{ % {year} {title} {institution} {???} {???} {comment}
\noindent{}{\bfseries #3}, {#2} \hfill {\itshape #1}\\[.25\baselineskip]
}

\newcommand{\cventry}[6]{ % {year} {title} {institution} {???} {department} {comment}
\noindent{}{\bfseries #3}, {#4} \hfill {\itshape #1}
\cvindent{#2}\\[.25\baselineskip]
}

\newcommand{\cventrywithcomment}[6]{ % {year} {title} {institution} {department} {???} {comment}
\noindent{}{\bfseries #3}, {#4}  \hfill {\itshape #1}
\cvindent{{#2} \hspace{.25em}\vrule width .75pt\hspace{.125em} {\itshape #6}}\\[.25\baselineskip]
}

\newcommand{\cvitem}[2]{
\noindent{}{\bfseries #2} \hfill {\itshape #1}\\[.25\baselineskip]
}

\newcommand{\cvitemwithcomment}[3]{
\noindent{}{\bfseries #2} \hfill {\itshape #1}\nopagebreak\\[.1\baselineskip]
\cvindent{{#3}}\\[.25\baselineskip]
}

\newcommand{\inlinecvitemwithcomment}[2]{
\noindent{}{\bfseries #1}---#2 \\[.25\baselineskip]
}


\usepackage{titlesec}
% section title formatting https://tex.stackexchange.com/a/40051
\titleformat{name=\section}[block]
  {\Large\bfseries\itshape\color{accent}}
  {} % before
  {0pt} % spacing
  {} % after
  [\hrule height 1pt]
\titlespacing*{\section}{0pt}{-.5\baselineskip}{0.2\baselineskip}

% draw orcid logo https://tex.stackexchange.com/a/445583
\usepackage{scalerel}
\usepackage{tikz}
\usetikzlibrary{svg.path}
\tikzset{
  orcidlogo/.pic={
    \fill[color2] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
    svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
    svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
  }
}

\newcommand\orcidicon{\mbox{\scalerel*{
        \begin{tikzpicture}[yscale=-1,transform shape]
          \pic{orcidlogo};
        \end{tikzpicture}
      }{|}}}

\begin{document}
\noindent{}\begin{minipage}[t]{.3\linewidth}
    {\Huge Mark Gillespie}\\
    {\Large \itshape \color{color2} \hspace*{.75em}Curriculum Vitae}
\end{minipage}
\hfill
\raisebox{10pt}{
\begin{minipage}[t][1.6cm][t]{.7\linewidth}
    \raggedleft
    \href{mailto:mark.gillespie@inria.fr}{mark.gillespie@inria.fr}\\
    \href{https://www.markjgillespie.com}{www.markjgillespie.com}\\
    \href{https://orcid.org/0009-0000-5645-9636}{\orcidicon{} 0009-0000-5645-9636}\\
    \href{https://scholar.google.com/citations?user=o_OqGM0AAAAJ}{\raisebox{-2pt}{\faGraduationCap{}} google scholar}\\
    \href{https://github.com/MarkGillespie/}{\faGithub{} MarkGillespie}
\end{minipage}}
\phantom{}\\[-.5\baselineskip]

% \makecvtitle
% \vspace{-3\baselineskip}

\section{Academic Appointments}
\cventry{To start July 2026}{Assistant Professor}{University of Utah}{Kahlert School of Computing}{}{}
\cventry{{Sept. 2024}--present}{Postdoctoral Researcher}{École Polytechnique / INRIA}{Laboratoire d'Informatique {\color{gray}[Computer Science Department]}}{}{}

\section{Education}
\cventrywithcomment{2018--2024}{PhD in Computer Science}{Carnegie Mellon University}{}{}{Advisor: Keenan Crane}\\[-1.3\baselineskip]
\cvindent{National Science Foundation Graduate Research Fellowship (NSF GRFP)}
%
\cventrywithcomment{2014--2018}{B.S. in Computer Science and B.S. in Mathematics}{California Institute of Technology}{}{}{Advisor: Peter Schröder}


% PUBLICATIONS ----------------------------------

\section{Journal Articles}
% use etaremune for reversed order
\begin{enumerate}[itemsep=.2\baselineskip, leftmargin=.5em, labelsep=1em, label={}]
\item \cvcite{Braune:2025:DTC}
\item \cvcite{Gillespie:2024:RTH}
\item \cvcite{Hirose:2024:SK}
\item \cvcite{Feng:2023:WND}
\item \cvcite{Liu:2023:SSI}
\item \cvcite{Gillespie:2021:ICI}
\item \cvcite{Gillespie:2021:DCE}
\end{enumerate}
\phantom{}\\[-\baselineskip]


\section{Other Refereed Publications}
% \section{Other Publications}
\begin{enumerate}[itemsep=.2\baselineskip, leftmargin=.5em, labelsep=1em, label={}]
\item \cvcite{Gillespie:2024:EIT}
\item \cvcite{Hirose:2024:SKA}
\item \cvcite{Sharp:2021:GPI}
\end{enumerate}
\phantom{}\\[-\baselineskip]

%----------------------------------
\section{Awards \& Honors}
\cvitemwithcomment{2024}{Two SIGGRAPH Best Paper Award Honorable Mentions}{Awarded to 12 papers out of about 840 submissions; $\sim$top 1.5\% of papers}
%
\cvitemwithcomment{2019-2022}{NSF Graduate Research Fellowship}{Awarded to top 15\% of applicants across all areas of science; \$147,000 over 3 years}
%
\cvitemwithcomment{2017}{Hertz Fellowship Finalist}{Awarded to top 5\% of applicants of applicants across applied science, math, and engineering.}
%
\cvitem{2016-2017}{Arthur R Adams SURF Fellow}{}
%
\cvitemwithcomment{2017}{SIGGRAPH ACM Turing Award Celebration Grant}{Awarded to 10 students in computer graphics from across the country.}
% \cvitemwithcomment{2016}{William Lowell Putnam Mathematics Competition }{31 points (rank: 365/3214)}


%----------------------------------
\section{Other Research Experience}

\cventrywithcomment{July 2023}{Visiting Researcher}{Technische Universit\"at Berlin}{Department of Mathematics}{}{Host: Boris Springborn}
%
\cventrywithcomment{Summer 2022}{Visiting Graduate}{University of California, San Diego}{Department of Computer Science and Engineering}{}{Host: Albert Chern}
%
\cventrywithcomment{Summer 2017}{Arthur R. Adams Undergraduate Researcher}{California Institute of Technology}{Department of Computing and Mathematical Sciences}{}
{Mentor: Peter Schr\"oder}
%
\cventrywithcomment{Summer 2016}{Arthur R. Adams Undergraduate Researcher}{California Institute of Technology}{Department of Computing and Mathematical Sciences}
{}
{Mentor: Mathieu Desbrun}
%
\cventrywithcomment{2016--2017}{Undergraduate Researcher}{California Institute of Technology}{Department of Computing and Mathematical Sciences}
{}
{Mentor: Alan Barr}
%

%----------------------------------
\section{Selected Talks}

\shortcventry
    {Sep. 2025}
    {{GeomeriX Seminar}}
    {Cellular Whitney Forms}
    {}{}{}
%
\shortcventry
    {May 2025}
    {\href{https://team.inria.fr/geomerix/seminars-2/}{GeomeriX Seminar}}
    {Geometry Processing with Intrinsic Triangulations}
    {}{}{}
%
\shortcventry
    {Apr. 2025}
    {\href{https://www.cgal.org/}{49th CGAL Developer Meeting}} %, Inria Sophia Antipolis
    {Geometry Processing with Intrinsic Triangulations}
    {}{}{}
%
\shortcventry
    {Apr. 2025}
    {\href{https://www.cgal.org/}{49th CGAL Developer Meeting}} %, Inria Sophia Antipolis
    {Ray Tracing Harmonic Functions}
    {}{}{}
%
\shortcventry
    {Feb. 2025}
    {\href{https://www.cs.utah.edu/}{University of Utah}}
    {New Foundations for Robust Geometry Processing}
    {}{}{}
%
\shortcventry
    {Feb. 2025}
    {\href{https://www.mfo.de/occasion/2506/www_view}{Oberwolfach Workshop on Surface Processing}}
    {Ray Tracing Harmonic Functions}
    {}{}{}
%
\shortcventry
    {Nov. 2024}
    {\href{https://visualcomputing.ist.ac.at/seminars/}{IST Austria}}
    {Solid Knitting \& Harmonic Hitting}
    {}{}{}
%
\shortcventry
    {Aug. 2024}
    {\href{https://s2024.conference-program.org/presentation/?id=papers_786&sess=sess128}{ACM SIGGRAPH 2024}}
    {Ray Tracing Harmonic Functions}
    {}{}{}
%
\shortcventry
    {Sept. 2023}
    {\href{https://visualcomputing.ist.ac.at/seminars/}{IST Austria}}
    {Intrinsic Triangulations in Geometry Processing}
    {}{}{}
%
\shortcventry
    {Aug. 2023}
    {\href{https://www.geometrie.tugraz.at/events/og2023.html}{Geometry Workshop in Obergurgl}}
    {Intrinsic Triangulations in Geometry Processing}
    {}{}{}
%
\shortcventry
    {Jul. 2023}
    {\href{https://www.discretization.de/events/14/}{TU Berlin SFB TRR 109 Colloquium}}
    {Intrinsic Triangulations in Geometry Processing}
    {}{}{}
%
\shortcventry
    {Apr. 2022}
    {\href{http://jacobsschool.ucsd.edu/visualcomputing/}{UCSD Pixel Cafe}}
    {Discrete Conformal Equivalence of Polyhedral Surfaces}
    {}{}{}
%
\shortcventry
    {Mar. 2022}
    {\href{https://www.youtube.com/watch?v=MLnswieg4Gw}{Toronto Geometry Colloquium}}
    {Discrete Conformal Equivalence of Polyhedral Surfaces}
    {}{}{}
%
\shortcventry
    {Nov. 2021}
    {\href{https://sa2021.siggraph.org/en/attend/technical-papers/8/session/55}{ACM SIGGRAPH Asia 2021}}
    {Integer Coordinates for Intrinsic Geometry Processing}
    {}{}{}
%
\shortcventry
    {Aug. 2021}
    {\href{https://s2021.siggraph.org/full-program/}{ACM SIGGRAPH 2021}}
    {Discrete Conformal Equivalence of Polyhedral Surfaces}
    {}{}{}
%
\shortcventry
    {Aug. 2021}
    {\href{https://dl.acm.org/doi/10.1145/3450508.3464592}{ACM SIGGRAPH 2021 Courses}}
    {Geometry Processing with Intrinsic Triangulations}
    {}{}{}
%
\shortcventry
    {June 2021}
    {\href{https://meshingroundtable.com/previous-imrs/}{SIAM IMR 2021 Courses}}
    {Geometry Processing with Intrinsic Triangulations}
    {}{}{}
%

\section{Service}

\inlinecvitemwithcomment{Technical Papers Committee}{SIGGRAPH (2026)}
%
\inlinecvitemwithcomment{Graduate School co-Chair}{Symposium on Geometry Processing (2026)}
%
\inlinecvitemwithcomment{Program Committee}{Symposium on Geometry Processing (2025)}
%
\inlinecvitemwithcomment{Reviewing}{SIGGRAPH (2019, 2022--2025), SIGGRAPH Asia (2022--2025), ACM Transactions on Graphics (2024--2025), Symposium on Geometry Processing (2025), Symposium on Computational Fabrication (2025), Graphics Replicability Stamp Initiative (2025), Eurographics (2024--2025), Computer Graphics Forum (2024), Pacific Graphics (2025), Journal of Computational and Applied Mathematics (2024--2025), Computer-Aided Design (2023), Transactions on Visualization and Computer Graphics (2023--2025), Computers \& Graphics (2021)}
%
\inlinecvitemwithcomment{Departmental Events}{
      Organizer, Graphics Reading Group (2022--2023);
      Organizer, Graphics Seminar (2020--2021);
      Panel Speaker (CSD Visit Day 2020, 2023, CSD Introductory Course 2022); Organizer, PhD mutual mentorship pod (2022--2024)}
%
\inlinecvitemwithcomment{Mentorship}{Summer Geometry Initiative volunteer (2024), Advising Master's student (2022-2023), CMU Summer Undergraduate Research Fellowship (2020)}
%

\section{Teaching Experience}

\cventry{Fall 2022}{Teaching Assistant}{CS 15-466/666: Computer Game Programming}{Carnegie Mellon University}{}{}
%
\cventry{Spring 2019}{Teaching Assistant}{CS 15-458/858: Discrete Differential Geometry}{Carnegie Mellon University}{}{}
%
\cventry{Fall 2017, 2018}{Teaching Assistant}{CS 171: Introduction to Computer Graphics}{California Institute of Technology}{}{}
%
\cventry{Spring 2016, 2017}{Teaching Assistant}{CS 38: Introduction to Algorithms}{California Institute of Technology}{}{}
%

\section{Press Coverage}

\shortcventry{Aug. 2024}{\href{https://creative.knittingindustry.com/solid-knitting-a-new-fabrication-technique/}{``Solid Knitting -- A New Fabrication Technique''}}{Knitting Industry Creative}{}{}{}
%
\shortcventry{Aug. 2024}{\href{https://textiletechsource.com/2024/08/12/solid-knitting-machine-builds-reconfigurable-objects/}{``Solid-Knitting Machine Builds Reconfigurable Objects''}}{Textile Technology Source}{}{}{}
%
\shortcventry{Aug. 2024}{\href{https://www.designboom.com/technology/machine-knitting-solid-furniture-3d-accessories-elastic-cord-yarn-carnegie-mellon-university-08-02-2024/}{``Carnegie Mellon University’s Researchers Develop `Solid Knitting'{}''}}{Design Boom}{}{}{}
%
\shortcventry{Aug. 2024}{\href{https://materialdistrict.com/article/solid-knitting-3d-printing-with-yarn/}{``Solid Knitting: 3D Printing with Yarn''}}{Material District}{}{}{}
%
\shortcventry{Jul. 2024}{
\href{https://cosmosmagazine.com/technology/computing/3d-knitting-could-make-solid-but-soft-furniture/}{``3D Knitting Could Make Solid But Soft Furniture''}}{Cosmos Magazine}{}{}{}
%
\shortcventry{Jul. 2024}{\href{https://interestingengineering.com/innovation/solid-knitted-three-dimensional-furniture-could-be-reality}{``Beware IKEA: Solid Knitted 3-Dimensional Furniture Could Be a Reality''}}{Interesting Engineering}{}{}{}
%
\shortcventry{Jul. 2024}{\href{https://newatlas.com/materials/solid-knitting-reconfigurable/}{``Innovative `Solid Knitting' Machine Builds 100\% Reconfigurable Objects''}}{New Atlas}{}{}{}
%
\shortcventry{Jul. 2024}{\href{https://www.msn.com/en-us/news/technology/solid-knitting-a-different-spin-on-3d-printing-that-can-make-furniture-out-of-yarn/ar-AA1ogaiP?ocid=BingNewsVerp}{``Solid Knitting: A Different Spin on 3D Printing That Can Make Furniture Out of Yarn''}}{ZME Science}{}{}{}
%
\shortcventry{Jul. 2024}{\href{https://blog.siggraph.org/2024/07/beyond-the-threads.html/}{``Beyond the Threads''}}{ACM SIGGRAPH Blog}{}{}{}
%
\shortcventry{Jul. 2024}{\href{https://www.cmu.edu/news/stories/archives/2024/july/robotics-institute-introduces-solid-knitting-as-new-fabrication-technique}{``Robotics Institute Introduces Solid Knitting as New Fabrication Technique''}}{CMU News}{}{}{}


  % ----------------------------------
  % \section{Programming Languages}
  % \cvitem{}{C++, Mathematica, Python, Java, Matlab, Haskell, Ocaml, \LaTeX}

\end{document}
